A hazards approach to the biometric analysis of infant mortality

### 2023-03-12 Slides/slides.Rmd
Fix yaml in slides

---
output:
   beamer_presentation:
      includes:
         before_body: gb_beforebody.txt
         in_header: gb_header.txt
      fig_caption: no
      fig_width: 5
      keep_tex: true  
fontsize: 16pt
author: Göran Broström
  G\"oran Brostr\"om, CEDAR, Ume{\aa} University \\
  {\small \faEnvelope: \url{gb@ehar.se}} \\
  {\small \faGithub:  \url{github.com/goranbrostrom}} \\
  {\small Web : \url{ehar.se}} \and
  \\ \\
    Tommy Bengtsson, Centre for Economic Demography, Lund University \\
    {\small \faEnvelope: \url{tommy.bengtsson@ekh.lu.se} \\
    {\small Web: \url{ehl.lu.se/kontakt/ekh-tbe}}}

---

@@

## Study area

\includegraphics[width=0.9\textwidth]{myfigs/vb.png}

>>>>

---
title: A hazards approach to the biometric analysis of infant mortality
author:
    - Göran Broström\inst{1}
    - Tommy Bengtsson\inst{2}
institute:
    - \inst{1}CEDAR, Umeå University (gb@ehar.se, https://github.com/goranbrostrom)
    - \inst{2}CED, Lund University (tommy.bengtsson@ekh.lu.se)
output:
  beamer_presentation:
    theme: Warsaw
---

@@

## Study area 1: Västerbotten 1861--1950

\includegraphics[width=0.8\textwidth]{myfigs/vb.png}
